Pool Model Paper

### 2023-12-08 pool_model.tex
add spatial figures

- \cite{emonet_agentcell_2005, gorochowski_bsim_2012, li_nufeb_2019, kreft_bacsim_1998}: examples of another toolboxes for bacterial communities modeling (ABM).\\
More about the modelling of the motile bacteria can be seen in works:~\cite{decoene_microscopic_2011, rosser_modelling_2014, sokolov_physical_2012, li_amplified_2008}.

>>>>

- \cite{emonet_agentcell_2005, gorochowski_bsim_2012, li_nufeb_2019, kreft_bacsim_1998}: examples of another toolboxes for bacterial communities modeling (ABM).\\
More about the modelling of the motile bacteria can be seen in works:~\cite{decoene_microscopic_2011, rosser_modelling_2014, sokolov_physical_2012, li_amplified_2008}.
\begin{figure}
    \includegraphics[width=0.5\textwidth]{Figures/snapshot_00000000.png}%
    \includegraphics[width=0.5\textwidth]{Figures/snapshot_00006500.png}\\
    \includegraphics[width=0.5\textwidth]{Figures/snapshot_00013000.png}%
    \includegraphics[width=0.5\textwidth]{Figures/snapshot_00020000.png}%
    \caption{}
    \label{fig:spatial-snapshots}
\begin{figure}
    \includegraphics[width=0.6\textwidth]{Figures/cell_growth.pdf}
    \caption{}
    \label{fig:spatial-growth-curve}
\begin{figure}
    \includegraphics[width=0.6\textwidth]{Figures/lag_phase.pdf}
    \caption{}
    \label{fig:spatial-lag-phase}
\begin{figure}
    \includegraphics[width=0.6\textwidth]{Figures/entropy.pdf}
    \caption{}
    \label{fig:spatial-entropy}
